\hspace{1cm} Do syntactic and semantic similarity lead to interference effects? \newline Evidence from self-paced reading and event-related potentials using German

### 2024-08-20 paper/main.tex
added missing commas

We sampled the free scaling parameter $F$ from a \textcolor{blue}{truncated normal prior distribution ($Normal_{lb=0,ub=0.05}(0.01, 0.01)$) with a lower bound of 0 and an upper bound of 0.05. This prior reflects the a priori belief that effect on the microvolt scale will range from 0 to 5 $\mu V$ with higher likelihood for effect sizes below 3 $\mu V$ (see Figure \ref{fig:model_predictions_ERP}). This relatively uninformative prior was chosen because although there exists no previously published ERP data on the Van Dyke (2007) design it reflects the reasonable range of effect sizes in psycholinguistic ERP research. In future work, the posterior distribution of the semantic interference effect in our ERP data, with range [-0.5, -0.1]\,$\mu V$, could be used as a basis for redefining a tighter prior on the scaling parameter $F$.} After sampling the scaling parameter, simulated data was generated from the model while holding all other parameters in the model at fixed values. \textcolor{blue}{We decided to model N400 amplitude differences because Bayes factors provided stronger evidence for the semantic interference effect on the N400 than on the P600 in the present ERP study. To reflect that larger predicted effect sizes correspond to more negative N400 amplitudes, the predicted effects from the model} were multiplied with $-1$.

>>>>

We sampled the free scaling parameter $F$ from a \textcolor{blue}{truncated normal prior distribution ($Normal_{lb=0,ub=0.05}(0.01, 0.01)$) with a lower bound of 0 and an upper bound of 0.05. This prior reflects the a priori belief that effect on the microvolt scale will range from 0 to 5 $\mu V$ with higher likelihood for effect sizes below 3 $\mu V$ (see Figure \ref{fig:model_predictions_ERP}). This relatively uninformative prior was chosen because, although there exists no previously published ERP data on the Van Dyke (2007) design, it reflects the reasonable range of effect sizes in psycholinguistic ERP research. In future work, the posterior distribution of the semantic interference effect in our ERP data, with range [-0.5, -0.1]\,$\mu V$, could be used as a basis for redefining a tighter prior on the scaling parameter $F$.} After sampling the scaling parameter, simulated data was generated from the model while holding all other parameters in the model at fixed values. \textcolor{blue}{We decided to model N400 amplitude differences because Bayes factors provided stronger evidence for the semantic interference effect on the N400 than on the P600 in the present ERP study. To reflect that larger predicted effect sizes correspond to more negative N400 amplitudes, the predicted effects from the model} were multiplied with $-1$.
